Panel Seminars

### 2021-05-03 about/about.Rmd
update
Updated Rmd files

---
layout: default
title: "About"
nav_order: 1
editor_options: 
  chunk_output_type: console
---

@@

# Rigorous, Reproducible Research in Marine Genomics

Welcome! We are a working group dedicated to promoting reproducible and robust genomic research in marine science and evolutionary biology.

## Organizers:

Katherine Silliman and Sam Bogan

## Faculty Mentors

Jon Puritz and Andrew Whitehead

## Working group members

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/website/about/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/website/about/about.Rmd")

>>>>

---
layout: default
title: "About"
nav_order: 2
editor_options: 
  chunk_output_type: console
---

@@

# About

Welcome! The MarineOmics working group is part of the RCN for Evolution in Changing Seas, and was formed to promote reproducible and robust genomic research in evolutionary biology and marine science. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices as obsolete. To support robust ‘omics research now and moving forward, the working group will disseminate guidelines through an easily-interfaced and dynamic website that will be deployed in August 2021. To help develop content for the website, we are hosting Q & A panel seminars with experts on various topics relating to ‘omics analyses in non-model systems.

The working group is also currently hosting three undergraduate research interns with funding from the RCN-ECS. These interns are part of a subgroup conducting a literature survey to characterize trends in data availability, code accessibility, and methods reproducibility for a peer-reviewed article.

@@

setwd("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/about/")
KnitPost("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/about/about.Rmd")

### 2021-05-03 index.Rmd
update
Updated Rmd files

# Welcome

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem.

@@

| Date        | Topic       | Panelists     |
| :---        | :---        | :---          |
| 5/7         | topic1      | [Katherine Silliman](https://ksilliman.weebly.com/)|
| 5/8         | topic2      | [Joe McGirr](https://joemcgirr.github.io./)|

# Contact

Katherine Silliman (email)
Sam Bogan (email)

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/website/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/website/index.Rmd")

>>>>

# About

The MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote reproducible and robust genomic research in marine science. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices as obsolete. To support robust 'omics research now and moving forward, the working group will disseminate guidelines through an easily-interfaced and dynamic website that will be deployed in August 2021. *Keep an eye on this URL for updates!*

@@

To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we are hosting Q & A panel seminars with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Seminars are every two weeks, on **Fridays from 11:00-12:15 US Central Time**. 3-5 expert panelists will discuss each topic, with questions coming from the working group and the audience. If you would like to submit a question for the panelists ahead of time, please send an email to rcnecs.marineomics[at]gmail.com .

Everyone is welcome to join!

**To receive a Zoom link, please fill out the registration form [here](
https://auburn.zoom.us/meeting/register/tZ0ode2rpz4sG9Il_TuYexWfqd6HyjdQ58Zi).**

@@

| Date        | Topic       | Panelists     |
| :---        | :---        | :---          |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   |
| May 21       |  WGS genotyping (low and high coverage)     | [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/), TBD |
| June 4       |  Population genomic analyses and filtering data     | TBD|
| June 18       |  Functional Genomics (RNAseq)     | TBD|

# Reproducibility in Marine Genomics  
The working group is also currently hosting three undergraduate research interns with funding from the [RCN-ECS](https://rcn-ecs.github.io/). These interns are part of a sub-committee conducting a literature survey to characterize trends in data availability, code accessibility, and methods reproducibility in papers that use genomics to study adaptation in marine systems. The results of this survey will be shared in a peer-reviewed article, along with guidance to improve the state of reproducibility in the field.  
# Working Group Members

#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), Auburn University - kes0132[at]auburn.edu
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara -snbogan[at]ucsb.edu
#### [Alan Downey-Wall](https://cos.northeastern.edu/people/alan-downey-wall/), Northeastern University 
#### Chris Mantegna, University of Washington  
#### [Danielle Davenport](https://www.researchgate.net/profile/Danielle-Davenport-2), University of Queensland  
#### [Hanny Rivera, PhD](https://www2.whoi.edu/staff/hrivera/), Woods Hole Oceanographic Institute  
#### Jecy Klinkam, College of William and Mary  
#### [Joe McGirr, PhD](https://joemcgirr.github.io/), UC-Davis 
#### Kaitlin Macaranas, CSU-Bakersfield 
#### Megan Guidry, University of Rhode Island
#### Natalie Ameral, University of Rhode Island & RI Dept. of Environmental Management 
#### [Sara Schaal](https://schaals.wixsite.com/smschaal), Northeastern University 
#### [Sara Wuitchik, PhD](https://sjswuitchik.weebly.com/), Harvard University

### Faculty Advisors
#### [Andrew Whitehead, PhD](https://whiteheadresearch.wordpress.com/), UC-Davis 
#### [Jon Puritz, PhD](https://www.marineevoeco.com/), University of Rhode Island 
#### [Steven Roberts, PhD](http://faculty.washington.edu/sr320/?page_id=10850), University of Washington

# Contact 
For more information about the working group or panel seminars, contact Katherine Silliman: kes0132[at]auburn.edu  
For more information about the reproducibility review and undergraduate internship, contact Sam Bogan: snbogan[at]ucsb.edu

@@

setwd("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/")
KnitPost("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/index.Rmd")
